\section{Defining Viazovska's Fourier Eigenfunctions}
\label{Ch4:Sec:Defs}

As we noted in \Cref{Ch3:Sec:Properties}, we construct our Fourier eigenfunctions as sums of integrals whose integrands obey several transformation properties. These transformation properties will be the result of well-known facts about modular forms, which we discussed in \Cref{Ch2:Sec:ModForms}. For each eigenfunction, we begin by defining families of functions---the $\phi$- and $\psi$-functions respectively---in terms of modular forms and associated functions. We then list their transformation rules, which we will apply throughout this chapter. We will end each subsection by defining their namesake eigenfunction.

\subsection{The $+1$-Eigenfunction}

We begin by defining the $\phi$-functions.

\begin{boxdefinition}[The $\phi$-Functions]\label{Ch4:Def:phis}
    Define the functions $\phi_0, \phi_{-2}, \phi_{-4} : \Halfplane \to \C$ by
    \begin{align}
        \phi_{-4} &:= \frac{E_4^2}{\Delta}
            \label{Ch4:Eq:phi_-4_def} \\
        \phi_{-2} &:= \frac{E_4\parenth{E_2 E_4 - E_6}}{\Delta}
            \label{Ch4:Eq:phi_-2_def} \\
        \phi_{0} &:= \frac{\parenth{E_2 E_4 - E_6}^2}{\Delta}
            \label{Ch4:Eq:phi_0_def}
    \end{align}
\end{boxdefinition}

Note first that these functions are holomorphic: their numerators are clearly holomorphic, as one can see from \Cref{Ch2:Sec:ModForms}, and we know that $\Delta$ does not vanish on the upper half-plane. We now give important transformation properties exhibited by these functions that will later allow us to change variables inside the integrands making up $a$. We only sketch the proof.

\begin{boxlemma}\label{Ch4:Lemma:phi_transformations}
    For all $z \in \Halfplane$,
    \begin{align}
        \phi_0\of{z + 1}
        &= \phi_0\of{z}
        \label{Ch4:Eq:phi_0_add_one} \\
        \phi_0\of{\frac{-1}{z}}
        &= \phi_0\of{z}
        - \frac{12 i}{\pi} \cdot \frac{1}{z} \cdot \phi_{-2}\of{z}
        - \frac{36}{\pi^2} \cdot \frac{1}{z^2} \cdot \phi_{-4}\of{z}
        \label{Ch4:Eq:phi_0_neg_inv}
    \end{align}
\end{boxlemma}
\begin{proof}[Proof sketch]
    \eqref{Ch4:Eq:phi_0_add_one} is immediate because all of the functions in the definition of $\phi_0$ are $1$-periodic---even $E_2$, despite not being a modular form, because of \Cref{Ch2:Lemma:E2_slash_action}. To prove \eqref{Ch4:Eq:phi_0_neg_inv}, since $E_4$, $E_6$ and $\Delta$ are level $1$ modular forms of weights $4$, $6$ and $12$ respectively, we know $E_4\of{\frac{-1}{z}} = z^4 E_4\of{z}$, $E_6\of{\frac{-1}{z}} = z^6 E_6\of{z}$ and $\Delta\of{\frac{-1}{z}} = z^{12} \Delta\of{z}$. We can also get an explicit formula for $E_2\of{\frac{-1}{z}}$ from \Cref{Ch2:Lemma:E2_slash_action}. Putting these together gives the desired result.
\end{proof}

We do not prove these here, but mention that they both follow from the weight $k$ slash action formulae on $E_k$ for $k \in \set{2, 4, 6}$. When $k = 4$ and $k = 6$, we have weight $k$ invariance, because $E_4$ and $E_6$ are modular forms, but when $k = 2$, we need to use \Cref{Ch2:Lemma:E2_slash_action}. A detailed proof of these transformations can be found in \cite{blueprint}. We now define the $+1$-eigenfunction $a$.

\begin{boxdefinition}[Viazovska's $+1$-Fourier Eigenfunction]\label{Ch4:Def:a}
    Define $a\rad : \R \to \C$ by
    \begin{align}
        a\rad\of{r} := I_1(r) + I_2(r) + I_3(r) + I_4(r) + I_5(r) + I_6(r)
            \label{Ch4:Eq:a_rad_def}
    \end{align}
    where, for all $r \in \R$,
    \begin{align}
        I_1(r) &:= \int_{-1}^{-1 + i} \phi_0\of{\frac{-1}{z+1}} \,
                                 \parenth{z + 1}^2 \,
                                 e^{\pi i r z} \,
                                 \diff{z}
            \label{Ch4:Eq:I_1_def} \\
        I_2(r) &:= \int_{-1 + i}^{i} \phi_0\of{\frac{-1}{z+1}} \,
                                 \parenth{z + 1}^2 \,
                                 e^{\pi i r z} \,
                                 \diff{z}
            \label{Ch4:Eq:I_2_def} \\
        I_3(r) &:= \int_{1}^{1 + i} \phi_0\of{\frac{-1}{z - 1}} \,
                                \parenth{z - 1}^2 \,
                                e^{\pi i r z} \,
                                \diff{z}
            \label{Ch4:Eq:I_3_def} \\
        I_4(r) &:= \int_{1 + i}^{i} \phi_0\of{\frac{-1}{z - 1}} \,
                                \parenth{z - 1}^2 \,
                                e^{\pi i r z} \,
                                \diff{z}
            \label{Ch4:Eq:I_4_def} \\
        I_5(r) &:= -2 \int_{0}^{i} \phi_0\of{\frac{-1}{z}} \,
                                z^2 \,
                                e^{\pi i r z} \,
                                \diff{z}
            \label{Ch4:Eq:I_5_def} \\
        I_6(r) &:= 2 \int_{i}^{i \infty} \phi_0\of{z} \,
                                e^{\pi i r z} \,
                                \diff{z}
            \label{Ch4:Eq:I_6_def}
    \end{align}
    Define the $+1$-Fourier eigenfunction $a : \R^8 \to \C$ by
    \begin{align}
        a(x) := a\rad\of{\norm{x}^2}
            \label{Ch4:Eq:a_def}
    \end{align}
\end{boxdefinition}

It is immediate from \eqref{Ch4:Eq:a_def} that $a$ is radial. All of its properties are determined by its radial part $a\rad$. There are similar definitions in Lean.

There is an important remark that must be made about the definitions in \eqref{Ch4:Eq:I_1_def}-\eqref{Ch4:Eq:I_6_def}: in the original paper \cite{Viazovska8}, the integrals $I_1$ and $I_2$ are combined, as are $I_3$ and $I_4$, and expressed in the following manner:
\begin{align*}
    I_1(r) + I_2(r) &= \int_{-1}^{i} \phi_0\of{\frac{-1}{z+1}} \, \parenth{z + 1}^2 \, e^{\pi i r z} \, \diff{z} \\
    I_3(r) + I_4(r) &= \int_{1}^{i} \phi_0\of{\frac{-1}{z - 1}} \, \parenth{z - 1}^2 \, e^{\pi i r z} \, \diff{z}
\end{align*}
with the contours not specified. The most `classical' choice would be quarter-circular contours, though the same results can be achieved working with straight and rectangular contours.

\begin{figure}[ht]
    \centering
    % First subfigure: quarter-circular contour
    \begin{subfigure}{0.3\textwidth}
        \centering
        \begin{tikzpicture}[scale=1.75]
            % Axes
            \draw[->] (-1.2,0) -- (1.2,0) node[right] {$\Re$};
            \draw[->] (0,-1.2) -- (0,1.2) node[above] {$\Im$};

            % Quarter-circle from -1 to i
            \draw[thick, domain=180:135, ->] plot ({cos(\x)}, {sin(\x)}) node[above left] {$I_1 + I_2$};
            \draw[thick, domain=135:90, -] plot ({cos(\x)}, {sin(\x)}) ;

            % Points of interest
            \labelledpoint{-1}{0}{0}{-0.8}{$-1$}
            \labelledpoint{0}{1}{0.25}{-0.4}{$i$}
        \end{tikzpicture}
        \label{Ch4:subfig:a_circ_contour}
        \caption{Quarter-Circular Contour}
    \end{subfigure}
    \hfill
    % Second subfigure: straight line
    \begin{subfigure}{0.3\textwidth}
        \centering
        \begin{tikzpicture}[scale=1.75]
            % Axes
            \draw[->] (-1.2,0) -- (1.2,0) node[right] {$\Re$};
            \draw[->] (0,-1.2) -- (0,1.2) node[above] {$\Im$};

            % Straight line from -1 to 1
            \draw[thick, ->] (-1,0) -- (-0.5,0.5) node[above left] {$I_1 + I_2$};
            \draw[thick, -] (-0.5,0.5) -- (0,1);

            % Points of interest
            \labelledpoint{-1}{0}{0}{-0.8}{$-1$}
            \labelledpoint{0}{1}{0.25}{-0.4}{$i$}
        \end{tikzpicture}
        \label{Ch4:subfig:a_lin_contour}
        \caption{Straight Line Contour}
    \end{subfigure}
    \hfill
    % Third subfigure: rectangular contour
    \begin{subfigure}{0.3\textwidth}
        \centering
        \begin{tikzpicture}[scale=1.75]
            % Axes
            \draw[->] (-1.2,0) -- (1.2,0) node[right] {$\Re$};
            \draw[->] (0,-1.2) -- (0,1.2) node[above] {$\Im$};

            % Rectangular contour
            \draw[thick, ->] (-1,0) -- (-1,0.5) node[left] {$I_1$};
            \draw[thick, -] (-1,0.5) -- (-1,1);
            \draw[thick, ->] (-1,1) -- (-0.5,1) node[above] {$I_2$};m
            \draw[thick, -] (-0.5,1) -- (0,1);

            % Points of interest
            \labelledpoint{-1}{0}{0}{-0.8}{$-1$}
            \labelledpoint{0}{1}{0.25}{-0.4}{$i$}
            \labelledpoint{-1}{1}{-0.7}{-0.2}{$-1 + i$}
        \end{tikzpicture}
        \label{Ch4:subfig:a_rect_contour}
        \caption{Rectangular Contour}
    \end{subfigure}
    \caption{\centering Different contours along which we can integrate the integrand of $I_1$ and $I_2$ to get an integral equal to $I_1 + I_2$}
    \label{Ch4:fig:a_contours}
\end{figure}

The reason the choice of contours does not matter is that the integrands of $I_1, \ldots, I_6$ are holomorphic on the upper half-plane. This is clear for $I_6$, and for the others, if we multiply terms of the form $\phi_0\of{\frac{-1}{z}}$ by $z^2$, apply \eqref{Ch4:Eq:phi_0_neg_inv} and multiply through, we end up with a holomorphic function.

The choice of rectangular contours (as in \Cref{Ch4:subfig:a_rect_contour}) as opposed to quarter-circles or straight lines for $I_1 + I_2$ and $I_3 + I_4$ is motivated by the versions of the Cauchy-Goursat Theorem that have been formalised in Lean. We discuss this further in \Cref{Ch5:Sec:Cauchy-Goursat}.

We are now ready to define the $-1$-eigenfunction $b$.

\subsection{The $-1$-Eigenfunction}
\label{Ch4:Subsec:b_def}

Recall the $H$-functions defined as the fourth powers of the Theta functions in \Cref{Ch2:Def:Theta_H}. We begin by defining the $h$ function, in terms of which we define the $\psi$-functions.

\begin{boxdefinition}[The $h$-Function]\label{Ch4:Def:h}
    Define the function $h : \Halfplane \to \C$ by
    \begin{align}
        h\of{z} := 128 \frac{H_3(z) + H_4(z)}{H_2(z)^2} \label{Ch4:Eq:h_def}
    \end{align}
    where $H_2$, $H_3$ and $H_4$ are as defined in \Cref{Ch2:Def:Theta_H}.
\end{boxdefinition}

In \cite{Viazovska8}, the $\psi$-functions are defined in terms of the $h$-function via slash actions.

\begin{boxdefinition}[The $\psi$-Functions]\label{Ch4:Def:psis_in_terms_of_h}
    Define the functions $\psi_I, \psi_S, \psi_T : \Halfplane \to \C$ by
    \begin{align*}
        \psi_I := h - h\mid_{-2} ST
        \qquad\qquad
        \psi_T := \psi_I \mid_{-2} T
        \qquad\qquad
        \psi_S := \psi_I \mid_{-2} S
    \end{align*}
    where $h$ is as defined in \Cref{Ch4:Def:h} and $I, S, T \in \SL{2, \Z}$ are as defined just before \Cref{Ch2:Prop:H_Rels}.
\end{boxdefinition}

It is possible to use the weight-$2$ slash action relations seen in \Cref{Ch2:Prop:H_Rels} to express the $\psi$-functions explicitly in terms of the $H$-functions.

\begin{boxlemma}\label{Ch4:Lemma:psi_explicitly}
    The $\psi$-functions can be expressed in the following manner:
    % Note that there's a missing - sign in the blueprint (need to fix ALL of the typos next week!)
    \begin{align*}
        \psi_I &= 128 \parenth{\frac{H_3 + H_4}{H_2^2} + \frac{H_4 - H_2}{H_3^2}} \\
        \psi_T &= 128 \parenth{\frac{H_3 + H_4}{H_2^2} + \frac{H_2 + H_3}{H_4^2}} \\
        \psi_S &= 128 \parenth{\frac{H_4 - H_2}{H_3^2} - \frac{H_2 + H_3}{H_4^2}}
    \end{align*}
\end{boxlemma}
\begin{proof}
    We prove the result for $\psi_I$ and sketch how to prove it for the others. Since $\psi_I = h - h \mid_{-2} ST$ and the first summand of $\psi_I$ given above is precisely $h$, we show that $h \mid_{-2} ST$ gives precisely the second summand.

    First, note that $j_{-2}\of{ST} = \parenth{z + 1}^2$. Observe that for all $z \in \Halfplane$, $\parenth{z + 1}^2 = \frac{\parenth{z + 1}^{-2}}{\parenth{\parenth{z + 1}^{-2}}^2}$. Hence,
    \begin{align*}
        h \mid_{-2} ST
        = 128 \frac{\parenth{H_3 \mid_2 ST} + \parenth{H_4 \mid_2 ST}}{\parenth{H_2 \mid_2 ST}^2}
        = 128 \frac{-\parenth{H_3 \mid_2 T} - \parenth{H_2 \mid_2 T}}{\parenth{-H_2 \mid_2 T}^2}
        = -128 \frac{H_4 - H_2}{H_3^2}
    \end{align*}
    with the second equality following from \Cref{Ch2:Lemma:Slash_Mul}. Subtracting $h \mid_{-2} ST$ from $h$ then gives the desired result. The explicit expressions for $\psi_T$ and $\psi_S$ can be obtained by performing similar computations on $\psi_I$.
\end{proof}

The proof of \Cref{Ch4:Lemma:psi_explicitly} shows us that weight $-2$ slash actions on the $\psi$-functions come directly from the analogous weight $2$ slash operations on the $H$-functions. We have seen several of these in \Cref{Ch2:Prop:H_Rels} and can combine them with \Cref{Ch2:Lemma:Slash_Mul} to generate the following relations between the $\psi$-functions.
\begin{align}
    \psi_T &= \psi_I \mid_{-2} T &
    \psi_T(z) &= \psi_I\of{z + 1}
    \label{Ch4:Eq:psi_T_eq_psi_I_add_one}
    \\
    \psi_I &= \psi_T \mid_{-2} T &
    \psi_I(z) &= \psi_T\of{z + 1}
    \label{Ch4:Eq:psi_I_eq_psi_T_add_one}
    \\
    \psi_S &= \psi_I \mid_{-2} S &
    \psi_S(z) &= z^2 \, \psi_I\of{\frac{-1}{z}}
    \label{Ch4:Eq:psi_S_eq_zsq_mul_psi_I_neg_inv}
    \\
    \psi_I &= \psi_S \mid_{-2} S &
    \psi_I(z) &= z^2 \psi_S\of{\frac{-1}{z}}
    \label{Ch4:Eq:psi_I_to_psi_S}
    \\
    \psi_S &= \psi_I \mid_{-2} S &
    \psi_S(z) &= z^2 \psi_I\of{\frac{-1}{z}}
    \label{Ch4:Eq:psi_S_to_psi_I}
    \\
    \psi_T &= \psi_S \mid_{-2} ST &
    \psi_T(z) &= \parenth{z+1}^2 \psi_S\of{\frac{-1}{z+1}}
    \label{Ch4:Eq:psi_T_to_psi_S_add}
    \\
    -\psi_{S} &= \psi_S \mid_{-2} T &
    -\psi_S(z) &= \psi_S(z + 1)
    \label{Ch4:Eq:psi_S_one_periodic}
    \\
    - \psi_{T} &= \psi_T \mid_{-2} S &
    - \psi_T(z) &= z^2 \psi_T\of{\frac{-1}{z}} \label{Ch4:Eq:psi_T_eq_zsq_mul_psi_T_neg_inv}
    \\
    - \psi_{T} &= \psi_I \mid_{-2} TS &
    - \psi_T(z) &= z^2 \psi_I\of{\frac{z - 1}{z}}
    \label{Ch4:Eq:psi_T_eq_neg_psi_I_slash_TS}
    \\
    - \psi_{T} &= \psi_S \mid_{-2} STS &
    - \psi_T(z) &= \parenth{z - 1}^2 \psi_S\of{\frac{-z}{z - 1}}
    \label{Ch4:Eq:psi_T_eq_neg_psi_S_slash_STS}
    \\
    \psi_{T} &= \psi_S \mid_{-2} TSTS &
    \psi_T(z) &= \parenth{z - 1}^2 \psi_S\of{\frac{-1}{z - 1}}
    \label{Ch4:Eq:psi_T_as_psi_S_for_J3_J4}
\end{align}
where we note that
\begin{align*}
    ST &= \begin{bmatrix}
        0 & -1 \\ 1 & 0
    \end{bmatrix}\begin{bmatrix}
        1 & 1 \\ 0 & 1
    \end{bmatrix} =  \begin{bmatrix}
        0 & -1 \\ 1 & 1
    \end{bmatrix} &
    TS &= \begin{bmatrix}
        1 & 1 \\ 0 & 1
    \end{bmatrix}\begin{bmatrix}
        0 & -1 \\ 1 & 0
    \end{bmatrix} = \begin{bmatrix}
        1 & -1 \\ 1 & 0
    \end{bmatrix} \\
    STS &= \begin{bmatrix}
        0 & -1 \\ 1 & 0
    \end{bmatrix}\begin{bmatrix}
        1 & -1 \\ 1 & 0
    \end{bmatrix} = \begin{bmatrix}
        -1 & 0 \\ 1 & -1
    \end{bmatrix} &
    TSTS &= \begin{bmatrix}
        1 & 1 \\ 0 & 1
    \end{bmatrix}\begin{bmatrix}
        -1 & 0 \\ 1 & -1
    \end{bmatrix} = \begin{bmatrix}
        0 & -1 \\ 1 & -1
    \end{bmatrix}
\end{align*}

It will be useful, particularly to prove Schwartzness, to express the $\psi$-functions in an alternate form, as fractions with the discriminant in the denominator. We can therefore express the $\psi$-functions in yet another form.

\begin{boxproposition}\label{Ch4:Prop:psi_as_div_disc}
    We can express $\psi_I, \psi_S, \psi_T$ in the following manner:
    \begin{align}
        \psi_I &= \frac{H_4^3\parenth{2 H_4^2 + 5 H_4 H_2 + 5 H_2^2}}{2 \Delta}
            \label{Ch4:Eq:psi_I_div_disc} \\
        \psi_S &= \frac{- H_2^3 \parenth{2 H_2^3 + 5 H_2 H_4 + 5 H_4^2}}{2 \Delta}
            \label{Ch4:Eq:psi_S_div_disc} \\
        \psi_T &= \psi_I - \psi_S
            \label{Ch4:Eq:psi_T_eq_psi_I_sub_psi_S}
    \end{align}
    where $\Delta$ is the discriminant form.
\end{boxproposition}

\eqref{Ch4:Eq:psi_I_div_disc} and \eqref{Ch4:Eq:psi_S_div_disc} can be proved by finding common denominators for the expressions in \Cref{Ch4:Lemma:psi_explicitly} and applying \eqref{Ch2:Eq:H_Jacobi} and \eqref{Ch2:Eq:Disc_H}. \eqref{Ch4:Eq:psi_T_eq_psi_I_sub_psi_S} is proved using slash actions, but we include it in \Cref{Ch4:Prop:psi_as_div_disc} because this gives us a clear way of seeing that the $\psi$-functions are holomorphic on the upper half-plane: $\Delta$ is holomorphic and non-vanishing, and the numerators are made entirely of holomorphic functions.

We are now ready to define the $-1$-eigenfunction, denoted $b$.

\begin{boxdefinition}[Viazovska's $-1$-Fourier Eigenfunction]\label{Ch4:Def:b}
    Define $b\rad : \R \to \C$ by
    \begin{align}
        b\rad\of{r} := J_1(r) + J_2(r) + J_3(r) + J_4(r) + J_5(r) + J_6(r)
        \label{Ch4:Eq:b_rad_def}
    \end{align}
    where, for all $r \in \R$,
    \begin{align}
        J_1(r) &:= \int_{-1}^{-1 + i} \psi_T\of{z} \,
                                 e^{\pi i r z} \,
                                 \diff{z}
            \label{Ch4:Eq:J_1_def} \\
        J_2(r) &:= \int_{-1 + i}^{i} \psi_T\of{z} \,
                                 e^{\pi i r z} \,
                                 \diff{z}
            \label{Ch4:Eq:J_2_def} \\
        J_3(r) &:= \int_{1}^{1 + i} \psi_T\of{z} \,
                                e^{\pi i r z} \,
                                \diff{z}
            \label{Ch4:Eq:J_3_def} \\
        J_4(r) &:= \int_{1 + i}^{i} \psi_T\of{z} \,
                                e^{\pi i r z} \,
                                \diff{z}
            \label{Ch4:Eq:J_4_def} \\
        J_5(r) &:= -2 \int_{0}^{i} \psi_I\of{z} \,
                                e^{\pi i r z} \,
                                \diff{z}
            \label{Ch4:Eq:J_5_def} \\
        J_6(r) &:= -2 \int_{i}^{i \infty} \psi_S\of{z} \,
                                e^{\pi i r z} \,
                                \diff{z}
            \label{Ch4:Eq:J_6_def}
    \end{align}
    Define the $-1$-Fourier eigenfunction $a : \R^8 \to \C$ by
    \begin{align}
        b(x) := b\rad\of{\norm{x}^2}
            \label{Ch4:Eq:b_def}
    \end{align}
\end{boxdefinition}

Note that by applying \eqref{Ch4:Eq:psi_T_to_psi_S_add} and \eqref{Ch4:Eq:psi_T_as_psi_S_for_J3_J4}, we can express $J_1, \ldots, J_5$ in the following manner:
\begin{align}
    J_1(r) &= \int_{-1}^{-1 + i} \psi_S\of{\frac{-1}{z + 1}} \, \parenth{z + 1}^2 \, e^{\pi i r z} \, \diff{z} \label{Ch4:Eq:J1_like_I1} \\
    J_2(r) &= \int_{-1 + i}^{i} \psi_S\of{\frac{-1}{z + 1}} \, \parenth{z + 1}^2 \, e^{\pi i r z} \, \diff{z} \label{Ch4:Eq:J2_like_I2} \\
    J_3(r) &= \int_{1}^{1 + i} \psi_S\of{\frac{-1}{z - 1}} \, \parenth{z - 1}^2 \, e^{\pi i r z} \, \diff{z} \label{Ch4:Eq:J3_like_I3} \\
    J_4(r) &= \int_{1 + i}^{i} \psi_S\of{\frac{-1}{z - 1}} \, \parenth{z - 1}^2 \, e^{\pi i r z} \, \diff{z} \label{Ch4:Eq:J4_like_I4} \\
    J_5(r) &= -2 \int_{0}^{i} \psi_S\of{\frac{-1}{z}} \, z^2 \, e^{\pi i r z} \, \diff{z} \label{Ch4:Eq:J5_like_I5}
\end{align}
With $J_1, \ldots, J_5$ expressed in this manner, and $J_6$ expressed as in \eqref{Ch4:Eq:J_6_def}, there are striking similarities between the $J_j$ and the $I_j$, with $\psi_S$ being the analogue of $\phi_0$. We can hence use similar approaches to prove properties about both $a$ and $b$. The differences in the signs between $J_3$ and $I_r$, $J_4$ and $I_4$, and $J_6$ and $I_6$, as well as the differences between the relations between the $\phi$- and $\psi$-functions, will account for the differences in the way we treat $a$ and $b$.