\section{Establishing the Schwartzness Property}
\label{Ch4:Sec:Schwartzness}

The magic function is a linear combination of $a$ and $b$, which are each defined as compositions of $a\rad$ and $b\rad$ with the norm-squared function. From \Cref{Ch3:Prop:Multidimensional_Schwartz_of_Schwartz}, we know that it is enough to establish that $a\rad$ and $b\rad$ are Schwartz to establish that $a$ and $b$ are Schwartz. In particular, this means the smoothness and decaying conditions need to be satisfied with respect to $\R$ inputs instead of $\R^8$ inputs, a substantial simplification. We can further simplify the problem by taking advantage of linearity.

We know that the Schwartz space is a $\C$-vector space, making it closed under addition. To show that $a\rad$ and $b\rad$ are Schwartz functions, we show that their constituent integrals $I_1, \ldots, I_6$ and $J_1, \ldots, J_6$ are Schwartz. We need to show both smoothness and rapid decay. Smoothness is fairly straightforward. Rapid decay, on the other hand, requires an additional ingredient.

It turns out that we can establish a an upper-bound for all functions of the form $\frac{f}{\Delta}$, where $\Delta$ is the discriminant form and $f$ admits a Fourier expansion whose coefficients grow polynomially.

\begin{boxtheorem}[{\cite[Lemma 7.4]{blueprint}}]\label{SP:PolyFourierCoeffBound}
    Let $f : \C \to \C$ be holomorphic. Denote by $c_f(n)$ its $n$th Fourier coefficient, with $c_f\of{n_0} \neq 0$, so that
    \begin{align*}
        f(z) = \sum_{n=n_0}^{\infty} c_f(n) \, e^{i \pi n z}
    \end{align*}
    If there exists $k \in \N$ such that $c_f(n) = \BigO{n^k}$ as $n \to \infty$, then there exists a constant $C_f > 0$ such that for all $z \in \Halfplane$ with $\Im\of{z} > 1/2$,
    \begin{align*}
        \abs{\frac{f(z)}{\Delta(z)}} \leq C_f \, e^{-\pi \parenth{n_0 - 2} \Im(z)}
    \end{align*}
\end{boxtheorem}
\begin{proof}
    Fix $z \in \Halfplane$ and assume $\Im(z) > 1/2$. Recall from \Cref{Ch2:Thm:Delta_Product_Formula} that $\Delta$ can be expressed as a (convergent) infinite product. We can hence write
    \begin{align*}
        \abs{\frac{f(z)}{\Delta(z)}}
        = \abs{\frac{\sum_{n = n_0}^{\infty} c_f(n) \, e^{\pi i n z}}{e^{2 \pi i z} \prod_{n=1}^{\infty} \parenth{1 - e^{2 \pi i n z}}^{24}}}
        = \abs{e^{\pi i \parenth{n_0 - 2} z}} \cdot \frac{\abs{\sum_{n=n_0}^{\infty} c_f(n) \, e^{\pi i \parenth{n - n_0} z}}}{\prod_{n=1}^{\infty} \abs{1 - e^{2 \pi i n z}}^{24}}
    \end{align*}
    Noting that $\abs{e^{iz}} = e^{-\Im(z)}$ and $\Im(z) > \frac{1}{2}$, we can see that
    \begin{align*}
        \abs{e^{\pi i \parenth{n_0 - 2} z}} \cdot \frac{\abs{\sum_{n=n_0}^{\infty} c_f(n) \, e^{\pi i \parenth{n - n_0} z}}}{\abs{\prod_{n=1}^{\infty} {1 - e^{2 \pi i n z}}^{24}}}
        \leq
        e^{-\pi \parenth{n - n_0} \Im(z)} \cdot \frac{\sum_{n=0}^{\infty} \abs{c_f(n)} \, e^{-\pi \parenth{n - n_0}/2}}{\abs{\prod_{n=1}^{\infty} {1 - e^{2 \pi i n z}}^{24}}}
    \end{align*}
    It has been \href{https://github.com/leanprover-community/mathlib4/blob/5a2eaa85c555c4263e15928cef249cbaad2eb2d2/Mathlib/Topology/Algebra/InfiniteSum/Order.lean#L379-L380}{verified formally} that the absolute value of a convergent infinite product is the product of the absolute values, and moreover, that the product of the absolute values is \href{https://github.com/leanprover-community/mathlib4/blob/5a2eaa85c555c4263e15928cef249cbaad2eb2d2/Mathlib/Topology/Algebra/InfiniteSum/Order.lean#L373-L374}{convergent}. It has also been \href{https://github.com/thefundamentaltheor3m/Sphere-Packing-Lean/blob/ba092be9cdebb1a9c170a22c234e71ca1842a173/SpherePacking/ForMathlib/tprod.lean#L28}{verified formally} that the infinite product is monotonic on convergent infinite products whose terms are nonnegative. Hence,
    \begin{align*}
        \abs{\prod_{n=1}^{\infty} \parenth{1 - e^{2 \pi i n z}}^{24}}
        = \prod_{n=1}^{\infty} \abs{1 - e^{2 \pi i n z}}^{24}
        \geq \prod_{n=1}^{\infty} \parenth{1 - e^{-2 \pi n \Im(z)}}^{24}
        \geq \prod_{n=1}^{\infty}\parenth{1 - e^{-\pi n}}^{24}
    \end{align*}
    We note that the third and fourth products are convergent because they are expressible, via the product formula, as $e^{2\pi\Im(z)} \Delta\of{i \cdot \Im(z)}$ and $e^{\pi} \Delta\of{i/2}$ respectively. Hence, defining
    \begin{align*}
        C_f := \frac{\sum_{n=0}^{\infty} \abs{c_f(n)} \, e^{-\pi \parenth{n - n_0}/2}}{\prod_{n=1}^{\infty}\parenth{1 - e^{-\pi n}}^{24}}
    \end{align*}
    we can see that $\abs{\frac{f(z)}{\Delta(z)}} \leq C_f \, e^{-\pi \parenth{n_0 - 2} \Im(z)}$, as desired.
\end{proof}

The purpose of the above is to bound the $\phi$- and $\psi$-functions using \Cref{SP:PolyFourierCoeffBound}. Since these functions are defined as sums and products of the Eisenstein series and the $H$-functions, whose Fourier series have the properties that
\begin{enumerate}
    \item the coefficients grow polynomially
    \item there is an index $n_0$ below which all Fourier coefficients are zero
\end{enumerate}
it is enough to show that sums and products of functions exhibiting this property inherit it. Note that this also explicitly establishes a fact we mentioned in passing in \Cref{Ch2:Subsec:ThetaFunctions}, where we argued that the Fourier coefficients of $H_3$ and $H_4$ grow polynomially because those of $\Theta_3$ and $\Theta_4$ do.

\begin{boxproposition}\label{Ch4:Prop:PolyGrowth_of_mul}
    Let $f_1, f_2 : \Halfplane \to \C$ be functions with (absolutely convergent) Fourier expansions
    \begin{align*}
        f_1(z) &= \sum_{n=n_1}^{\infty} c_1(n) \, e^{\pi i n z} \\
        f_2(z) &= \sum_{n=n_2}^{\infty} c_2(n) \, e^{\pi i n z}
    \end{align*}
    such that for $i \in \set{1, 2}$, $c_i(n_i) \neq 0$ and $\exists k_i \in \N$ such that $c_i(n) = \BigO{n^{k_i}}$ as $n \to \infty$. Then, their product $f_1 f_2$ is expressible as an absolutely convergent Fourier series
    \begin{align*}
        f_1(z) f_2(z) &= \sum_{n = n_1 + n_2}^{\infty} c(n) \, e^{\pi i n z}
    \end{align*}
    such that $c(n_1 + n_2) \neq 0$ and $\exists k \in \N$ such that $c(n) = \BigO{n^k}$ as $n \to \infty$.
\end{boxproposition}
\begin{proof}
    Fix $z \in \Halfplane$. Then, due to absolute convergence, we can write
    \begin{align*}
        f_1(z) f_2(z) &= \parenth{\sum_{n=n_1}^{\infty} c_1(n) \, e^{\pi i n z}} \parenth{\sum_{m=n_2}^{\infty} c_2(m) \, e^{\pi i m z}} \\
        &= \sum_{n = n_1}^{\infty} \sum_{m = n_2}^{\infty} c_1(n) c_2(m) \, e^{\pi i \parenth{n + m} z}
    \end{align*}
    The smallest value of $m + n$ is clearly $n_1 + n_2$. Denoting this by $n_0$, we can write
    \begin{align*}
        f_1(z) f_2(z) &= \sum_{\ell = n_0}^{\infty} c(n) \, e^{\pi i \ell z}
    \end{align*}
    where for each $\ell \geq n_0$, $c(\ell)$ is a sum of finitely many terms of the form $c_1(n) c_2(m)$, with $n + m = \ell$. Now, we know there exist positive numbers $C, D \in \R$ and $N, M \in \N$ such that for all $n \geq N$ and $m \geq M$, $\abs{c_1(n)} \leq C \abs{n^{k_1}} = C n^{k_1}$ and $\abs{c_2(m)} \leq D \abs{m^{k_2}} = D m^{k_2}$. Defining
    \begin{align*}
        C' := \sum_{n=n_1}^{N} \abs{c_1(n)}
        \qquad \qquad
        D' := \sum_{m=n_2}^{M} \abs{c_2(m)}
    \end{align*}
    we can bound $\abs{c(\ell)}$ above by a sum of finitely many terms of the form $C' \abs{c_2(m)}$, $D' \abs{c_1(n)}$, and $\abs{c_1(n)} \cdot \abs{c_2(m)}$, with $n \geq N$ and $m \geq M$. Take $k = k_1 + k_2$. Then, $\abs{c_1(n)} \leq C n^{k_1} \leq C \parenth{m+n}^{k_1}$ and $\abs{c_2(n)} \leq D m^{k_2} \leq D \parenth{m+n}^{k_2}$, so $c(\ell) = \BigO{\parenth{m+n}^{k_1 + k_2}} = \BigO{\ell^k}$. % As Jaimin pointed out, max(k_1, k_2) should also be ok.
\end{proof}

The analogous result for sums is clear, with $n_0 \geq \min\of{n_1, n_2}$ and $k = \max\of{k_1, k_2}$. Note that for sums, $n_0$ may not be exactly $\min\of{n_1, n_2}$ because the Fourier coefficients of smallest index may cancel each other out. For the remainder of this thesis, we use the following notation.

\begin{boxnotation}
    For a function $f$ with a Fourier expansion, denote by
    \begin{itemize}
        \item $n_0\of{f}$ the smallest index $n$ such that $c_f(n) \neq 0$ (if it exists)
        \item $c_f(n)$ the $n$th Fourier coefficient of $f$
    \end{itemize}
    We will not use this notation for functions for which $n_0\of{f}$ does not exist.
\end{boxnotation}

In the following subsections, we apply the above results and show that $a\rad$ and $b\rad$ are Schwartz functions. In each case, since the bound in \Cref{SP:PolyFourierCoeffBound} is given in terms of $n_0$, we compute the values of $n_0$ explicitly.

\subsection{The $+1$-Eigenfunction}
\label{Ch4:Subec:Schwartzness_a}

We begin by proving that $I_1, \ldots, I_6$ are smooth. The key to proving this is the Leibniz Integral Rule\footnote{Also known as Leibniz's technique for `differentiating under the integral sign'}, which states that under mild conditions, the derivative with respect to one variable of the integral with respect to the other variable of a function of two variables is given by the integral of the corresponding partial derivative, which implies the analogous differentiability criterion.

\begin{boxlemma}\label{Ch4:Lemma:Ij_Smooth}
    For all $1 \leq j \leq 6$ and $k \in \N$, $I_j(r)$ is $k$ times differentiable.
\end{boxlemma}
\begin{proof}
    Fix $1 \leq j \leq 6$. We know, from \Cref{Ch4:Def:a}, that
    \begin{align*}
        I_j(r) = \int_{X_j} g_j\of{z} \, e^{\pi i r z} \, \diff{z}
    \end{align*}
    for intervals $X_j$ and holomorphic functions $g_j : \Halfplane \to \C$. The Leibniz Integral Rule then tells us that for all $k \in \N$, the $k$th derivative of $I_j$ at some $r \in \R$ is given by
    \begin{align}
        \int_{X_j} g_j\of{z} \, \parenth{\pi i z}^{k} \, e^{\pi i r z} \, \diff{z}
        \label{Ch4:Eq:Ij_deriv}
    \end{align}
    In particular, $I_j$ is smooth (in $r$) for all $j$.
\end{proof}

We are now ready to prove that $I_1, \ldots, I_6$ and their derivatives satisfy the decaying property. As a first step, we show that we can apply \Cref{SP:PolyFourierCoeffBound}.

\begin{boxlemma}\label{Ch4:Lemma:PolyFourierCoeffBound_Apply_a}
    There exist real numbers $C_0, C_{-2}, C_{-4} > 0$ such that
    \begin{align}
        \abs{\phi_0\of{z}} &\leq C_{0} e^{-2\pi\Im(z)}  
            \label{Ch4:Eq:PolyFourierCoeffBound_phi_0} \\
        \abs{\phi_{-2}\of{z}} &\leq C_{-2}  
            \label{Ch4:Eq:PolyFourierCoeffBound_phi_neg_2} \\
        \abs{\phi_{-4}\of{z}} &\leq C_{-4} e^{2\pi\Im(z)}
            \label{Ch4:Eq:PolyFourierCoeffBound_phi_neg_4}
    \end{align}
    for all $z \in \Halfplane$ with $\Im(z) > \frac{1}{2}$.
\end{boxlemma}
\begin{proof}
    Fix $z \in \Halfplane$ and assume that $\Im(z) > 1/2$. Since the Fourier coefficients of $E_2$, $E_4$ and $E_6$ grow polynomially (see \Cref{Ch2:Thm:E2_qexpansion,Ch2:Thm:Ek_qexpansion}), by \Cref{Ch4:Prop:PolyGrowth_of_mul}, the Fourier coefficients of the numerators of $\phi_0$, $\phi_{-2}$ and $\phi_{-4}$ grow polynomially as well. All that remains is to compute $n_0$ for the numerators of $\phi_0$, $\phi_{-2}$ and $\phi_{-4}$. Denote these $N_0$, $N_{-2}$ and $N_{-4}$ respectively. Note that $n_0\of{E_2} = n_0\of{E_4} = n_0\of{E_6} = 0$, with $c_{E_2}\of{0} = c_{E_4}\of{0} = C_{E_6}\of{0} = 1$.

    \begin{itemize}
        \item \underline{$N_0 = 4$.} Recall that the numerator of $\phi_0$ is $\parenth{E_2 E_4 - E_6}^2$. \Cref{Ch4:Prop:PolyGrowth_of_mul} then tells us that $n_0\of{E_2 E_4} = 0$. So, $n_0\of{E_2 E_4 - E_6} \geq 0$. In fact, the $0$th coefficients of both $E_2 E_4$ and $E_6$ are $1$, so they cancel. Hence, $n_0\of{E_2 E_4 - E_6} = 2$. Hence, by $n_0\of{\parenth{E_2 E_4 - E_6}^2} = 4$.
        
        \item \underline{$N_{-2} = 2$.} Recall that the numerator of $\phi_{-2}$ is $E_4\parenth{E_2 E_4 - E_6}$. $n_0\of{E_2 E_4 - E_6} = 2$ as shown above. Hence, $n_0\of{E_4\parenth{E_2 E_4 - E_6}} = 2$.
        
        \item \underline{$N_{-4} = 0$.} Recall that the numerator of $\phi_0$ is $E_4^2$. Hence, $n_0\of{E_4^2} = 0$.
    \end{itemize}
    Substituting these values into \Cref{SP:PolyFourierCoeffBound} then gives us the desired bounds.
    \begin{comment}
    The following is a consequence of a result proved by Ramanujan \todo{find citation for original paper} in the theory of (quasi-)modular forms:
    \begin{align}
        E_2 E_4 - E_6 &= 720 \sum_{n=1}^{\infty} n \, \sigma_3(n) \, e^{2\pi i nz}
        \label{Ch4:Eq:E2E4_sub_E6_qexpansion}
    \end{align}
    with the sum converging absolutely. Furthermore, it is easily seen that $\sigma_3(n) = \BigO{n^4}$, since $\sigma_3(n)$ is the sum of at most $n$ elements that are each at most $n^3$. Then, combining \eqref{Ch4:Eq:E2E4_sub_E6_qexpansion} and \eqref{Ch2:Eq:E4_qexpansion}, one can show that $E_4^2$, $E_4\parenth{E_2 E_4 - E_6}$, and $\parenth{E_2 E_4 - E_6}$ all have Fourier expansions in which each Fourier coefficient is $\BigO{n^{10}}$. For instance, we know
    \begin{align}
        \parenth{E_2 E_4 - E_6}^2 = 720^2 \sum_{m=1}^{\infty} \sum_{n=1}^{\infty} n \, \sigma_3(n) \, e^{2\pi i z \parenth{m + n}}
        \label{Ch4:Eq:E2E4_sub_E6_sq_qexpansion}
    \end{align}
    The Fourier coefficient corresponding to a term of the form $e^{2 \pi i z \parenth{m + n}}$ is a sum of at most $m + n$ terms that are each bounded above by $\parenth{\parenth{m + n}\sigma_3\of{m + n}}^2$, which is $\BigO{\parenth{m + n}^{10}}$. Similar computations can be performed for $E_4^2$ and $E_4\parenth{E_2 E_4 - E_6}$, proving that the polynomial growth assumption of \Cref{SP:PolyFourierCoeffBound} is satisfied by $\phi_{-4}$, $\phi_{-2}$ and $\phi_0$.

    We also note from \eqref{Ch4:Eq:E2E4_sub_E6_sq_qexpansion} that the smallest nonzero Fourier coefficient corresponds to $m + n = 2$. Reconciling this with the fact that in the statement of \Cref{SP:PolyFourierCoeffBound}, we express the Fourier series in terms of powers of $e^{\pi i z}$ and not $e^{2 \pi i z}$, we conclude that the right choice of $n_0$ to bound $\phi_0$ is $4$. Similar computations show that the right value for $\phi_{-2}$ is $2$ and that for $\phi_{-4}$ is $0$, which allows us to apply \Cref{SP:PolyFourierCoeffBound} and conclude that there exist $C_0, C_{-2}, C_{-4} > 0$ such that
    \begin{align*}
        \abs{\phi_0\of{z}} &\leq C_{0} e^{-2\pi\Im(z)} \\
        \abs{\phi_{-2}\of{z}} &\leq C_{-2} \\
        \abs{\phi_{-4}\of{z}} &\leq C_{-4} e^{2\pi\Im(z)}
    \end{align*}
    as required.
    \end{comment}
\end{proof}

We can now bound $I_1$, $I_3$ and $I_5$.

\begin{boxlemma}\label{Ch4:Lemma:Bound_I1_I3_I5}
    There exists a positive real number $C_0$ such that for all $r \in \R$,
    \begin{align*}
        \abs{I_1(r)}, \abs{I_3(r)}, \abs{I_5(r)} &\leq \int_{1}^{\infty} C_0 \, e^{-2\pi s} \, e^{-\pi r/s} \, \diff{s}
    \end{align*}
\end{boxlemma}
\begin{proof}
    For conciseness, we only bound $\abs{I_1}$ explicitly. Parametrise $z = -1 + it$ in \eqref{Ch4:Eq:I_1_def}. Then, for all $r \in \R$, we can write
    \begin{align*}
        I_1(r) &= -i \int_{0}^{1}
            \phi_0\of{\frac{-1}{it}} \,
            t^2 \,
            e^{-\pi i r} \,
            e^{\pi r t}\,
            \diff{t}
    \end{align*}
    Writing $s = \frac{1}{t}$ and simplifying, we get that
    \begin{align*}
        I_1(r) &= -i \int_{1}^{\infty}
            \phi_0\of{is} \,
            s^{-4} \,
            e^{-\pi i r} \,
            e^{-\pi r / s}\,
            \diff{t}
    \end{align*}
    Applying the triangle inequality, multiplicativity and monotonicity, we get
    \begin{align*}
        \abs{I_1(r)} &\leq \int_{1}^{\infty} \abs{
            \phi_0\of{is} \,
            s^{-4} \,
            e^{-\pi i r} \,
            e^{-\pi r / s}\,
            } \diff{t}
        \leq \int_{1}^{\infty}
            \abs{\phi_0\of{is}} \,
            e^{-\pi i r/s}
    \end{align*}
    Since $s > \frac{1}{2}$ inside the integral, we know from \Cref{Ch4:Lemma:PolyFourierCoeffBound_Apply_a} that $\exists C_0 > 0$ such that
    \begin{align*}
        \abs{I_1(r)} \leq \int_{1}^{\infty} C_0 \, e^{-2\pi s} \, e^{-\pi r/s} \, \diff{s}
    \end{align*}
    as required. The bounds on $\abs{I_3}$ and $\abs{I_5}$ are computed similarly.
\end{proof}

Now that we have bounds on the integrals with bounded vertical contours, we compute bounds on the integrals with bounded horizontal contours.

\begin{boxlemma}\label{Ch4:Lemma:Bound_I2_I4}
    There exists a positive real number $C_1$ such that for all $r \in \R$,
    \begin{align*}
        \abs{I_2(r)}, \abs{I_4(r)} &\leq C_1 \, e^{-\pi r}
    \end{align*}
\end{boxlemma}
\begin{proof}
    For conciseness, we only bound $\abs{I_2}$ explicitly. Parametrise $z = -1 + t + i$ in \eqref{Ch4:Eq:I_2_def}. Then, for all $r \in \R$, we can write
    \begin{align*}
        I_2(r) = \int_{0}^{1}
            \phi_0\of{\frac{-1}{t + i}} \,
            \parenth{t + i}^2 \,
            e^{-\pi i r} \,
            e^{\pi i r t} \,
            e^{-\pi r} \,
            \diff{t}
    \end{align*}
    Applying the triangle inequality, multiplicativity and monotonicity, we get
    \begin{align*}
        \abs{I_2(r)} &\leq \int_{0}^{1} \abs{\phi_0\of{\frac{-1}{t + i}}} \cdot 2e^{-\pi r} \, dt
    \end{align*}
    It is therefore enough to show that \Cref{SP:PolyFourierCoeffBound} applies. To that end, we manipulate the expression inside $\phi_0$:
    \begin{align*}
        \frac{-1}{t + i} = \frac{t}{t^2 + 1} + \frac{1}{t^2 + 1}i
    \end{align*}
    From this, we can deduce that its imaginary part is greater than $\frac{1}{2}$ for all $t \in \parenth{0, 1}$. Then, \Cref{SP:PolyFourierCoeffBound} tells us that $\exists C_0 > 0$ such that
    \begin{align*}
        \abs{\phi_0\of{\frac{-1}{t + i}}}
        \leq C_0 \, e^{-2 \pi \cdot \frac{1}{t^2 + 1}}
        \leq C_0 \, e^{-2\pi \cdot \frac{1}{2}} = C_0 \, e^{-\pi}
    \end{align*}
    Then, taking $C_1 := 2 \, C_0 \, e^{-\pi}$ and applying monotonicity,
    \begin{align*}
        \abs{I_2(r)} \leq \int_{0}^{1} C_1 \, e^{-\pi r} \, \diff{t} = C_1 \, e^{-\pi r}
    \end{align*}
    as required. The bound on $\abs{I_4}$ is computed similarly.
\end{proof}

Finally, we bound the integral with the unbounded vertical contour.

\begin{boxlemma}\label{Ch4:Lemma:Bound_I6}
    There exists a positive real number $C_2$ such that for all $r \in \R$,
    \begin{align*}
        \abs{I_6(r)} &\leq C_2 \, \frac{e^{-\pi \parenth{r + 2}}}{r + 2}
    \end{align*}
\end{boxlemma}
\begin{proof}
    Parametrise $z = it$ in \eqref{Ch4:Eq:I_6_def}. Then, for all $r \in \R$, we can write
    \begin{align*}
        I_6(r) &= -2i \int_{1}^{\infty} \phi_0\of{it} \, e^{- \pi r t} \, \diff{t}
    \end{align*}
    Applying the triangle inequality, multiplicativity and monotonicity, we get
    \begin{align*}
        \abs{I_6(r)} \leq 2\int_{1}^{\infty}
            \abs{\phi_0\of{it}} \,
            e^{-\pi r t} \,
            \diff{t}
    \end{align*}
    Let $C_0$ be as in \Cref{SP:PolyFourierCoeffBound} and define $C_1 := 2 C_0$. Then,
    \begin{align*}
        \abs{I_6(r)} \leq 2\int_{1}^{\infty}
            C_0 \,
            e^{-2 \pi t} \,
            e^{-\pi r t} \,
            \diff{t}
        = C_1 \int_{1}^{\infty} e^{-\parenth{2\pi + \pi r}t} \, \diff{t}
        = C_1 \frac{e^{-\pi\parenth{r + 2}}}{\pi\parenth{r + 2}}
    \end{align*}
    Defining $C_2 := \frac{C_1}{\pi}$ then yields the desired result.
\end{proof}

The formal proofs of the bounds in \Cref{Ch4:Lemma:Bound_I1_I3_I5,Ch4:Lemma:Bound_I2_I4,Ch4:Lemma:Bound_I6} are complete up to proofs that they are bounded by integrable functions, which is necessary to apply monotonicity of the integral due to the definition of the integral in \mathlib. The evaluation of the final integral in \Cref{Ch4:Lemma:Bound_I6} is also currently a \sorry.\todo{Update}

We now demonstrate how bounds on higher derivatives of $I_1$ can be reduced to the case we saw in \Cref{Ch4:Lemma:Bound_I1_I3_I5}.

\begin{boxlemma}
    For all $k \in \N$, there exists a positive real number $C_0^{(k)}$ such that for all $r \in \R$,
    \begin{align*}
        \abs{I_1^{(k)}\of{r}} \leq \int_{1}^{\infty} C_0^{(k)} \, e^{-2\pi s} \, e^{- \pi r / s} \, \diff{s}
    \end{align*}
\end{boxlemma}
\begin{proof}
    Fix $k \in \N$ and $r \in \R$. As we showed in \eqref{Ch4:Eq:Ij_deriv}, the $k$th derivative of $I_1$ at $r$ can be expressed as
    \begin{align*}
        I_1^{(k)}\of{r} = \int_{-1}^{-1+i} \phi_0\of{\frac{-1}{z+1}} \, \parenth{z+1}^2 \, \parenth{\pi i z}^k \, e^{\pi i r z} \, \diff{z}
    \end{align*}
    Parametrise $z = -1 + it$. Then,
    \begin{align*}
        I_1^{(k)}\of{r} = -i \int_{0}^{1} \phi_0\of{\frac{-1}{it}} \, t^2 \, \parenth{-\pi i - \pi t}^k \, e^{-\pi i r} \, e^{\pi r t} \, \diff{z}
    \end{align*}
    Writing $s = \frac{1}{t}$ and simplifying, we get that
    \begin{align*}
        I_1^{(k)}\of{r} &= -i \int_{1}^{\infty}
            \phi_0\of{is} \,
            s^{-4} \,
            \parenth{-\pi i - \frac{\pi}{s}}^k \,
            e^{-\pi i r} \,
            e^{-\pi r / s}\,
            \diff{t}
    \end{align*}
    Observe that for all $s \in \Ico{1, \infty}$,
    \begin{align*}
        \abs{-\pi i - \frac{\pi}{s}} = \pi \abs{i + \frac{1}{s}} \leq \pi \sqrt{2}
    \end{align*}
    Combining this with the bound computed in the proof of \Cref{Ch4:Lemma:Bound_I1_I3_I5}, we know $\exists C_0 > 0$ such that
    \begin{align*}
        \abs{I_1^{(k)}\of{r}} \leq \int_{1}^{\infty} C_0 \parenth{\pi \sqrt{2}}^{k} \, e^{-2\pi s} \, e^{- \pi r / s} \, \diff{s}
    \end{align*}
    Defining $C_0^{(k)} := C_0 \parenth{\pi \sqrt{2}}^{k}$ then gives the desired result.
\end{proof}

Analogous results can be proved for the other $I_j$, with any arising constants subsumed into the constants defined in \Cref{Ch4:Lemma:Bound_I1_I3_I5,Ch4:Lemma:Bound_I2_I4,Ch4:Lemma:Bound_I6}. Therefore, if we can show that the functions (without the constants) on the right-hand sides of \Cref{Ch4:Lemma:Bound_I1_I3_I5,Ch4:Lemma:Bound_I2_I4,Ch4:Lemma:Bound_I6} decay faster than any inverse power of $r$, we will have the result.

%%%%%%%% THE FOLLOWING WAS ACCIDENTALLY DELETED DURING AN UNSAFE GITHUB MERGE. BE CAREFUL WHEN SWITCHING FROM OVERLEAF TO LOCAL AND BACK!

It is clear that the estimates for $\abs{I_2}$, $\abs{I_4}$ and $\abs{I_6}$ have at least exponential decay, making them more rapidly decaying than any inverse power of $r$. This is less clear $\abs{I_1}$, $\abs{I_3}$ and $\abs{I_5}$. In these cases, the result is actually a consequence of a deeper result involving the Gamma function that has been formalised in \mathlib. We give a proof below.

\begin{boxlemma}
    For all $n \in \N$, there exists a constant $C'$ such that for all $r \in \R$,
    \begin{align*}
        \abs{r}^n \cdot \int_{1}^{\infty} e^{-2\pi s} \, e^{-\pi r /s} \, \diff{s} \leq C'
    \end{align*}
\end{boxlemma}
\begin{proof}
    Fix $n \in \N$. Observe that the map $x \mapsto e^{-\pi x}$ is Schwartz, meaning that there exists a constant $C$ such that for all $x \in \R$, $\abs{x}^n \cdot \abs{e^{-\pi x}} \leq C$. In particular, for all $r \in \R$ and $s \geq 1$,
    \begin{align*}
        \abs{r}^n \cdot e^{-\pi r/s} \leq C s^n
    \end{align*}
    Hence, for all $r \in \R$, we can write
    \begin{align*}
        \abs{r}^n \cdot \int_{1}^{\infty} e^{-2\pi s} \, e^{-\pi r /s} \, \diff{s}
        = \int_{1}^{\infty} e^{-2\pi s} \, \parenth{\abs{r}^n \cdot e^{-\pi r /s}} \, \diff{s}
        \leq C \int_{1}^{\infty} e^{-2\pi s} \, s^n \, \diff{s}
    \end{align*}
    It is \href{https://github.com/leanprover-community/mathlib4/blob/5a2eaa85c555c4263e15928cef249cbaad2eb2d2/Mathlib/Analysis/SpecialFunctions/Gamma/Basic.lean#L403}{known in \mathlib} that the $\Gamma$ function is given by
    \begin{align*}
        \Gamma(x) = \int_{0}^{\infty} e^{-u} \, u^{x-1} \, \diff{u}
    \end{align*}
    for all $x > 0$. Hence, writing $u = 2\pi s$ and \href{https://github.com/leanprover-community/mathlib4/blob/5a2eaa85c555c4263e15928cef249cbaad2eb2d2/Mathlib/Analysis/SpecialFunctions/Gamma/Basic.lean#L430}{relating $\Gamma$ with the factorial}, we get
    \begin{align*}
        C \int_{1}^{\infty} e^{-2\pi s} \, s^n \, \diff{s}
        = C \int_{1}^{\infty} \frac{1}{\parenth{2\pi}^{n+1}} e^{-u} \, u^n \, \diff{u}
        = \frac{C}{\parenth{2\pi}^n} \Gamma\of{n + 1}
        = \frac{C \cdot n!}{\parenth{2\pi}^n}
    \end{align*}
    Defining $C' := \frac{C \cdot n!}{\parenth{2\pi}^n}$ finishes the proof.
\end{proof}

An important comment we make here is that the fact that the functions that the bounding functions decay also shows that the integrals $I_j$ converge absolutely. In particular, their integrands are integrable.

In summary, we have shown that the $\R \to \C$ function $a\rad = I_1 + \cdots + I_6$ is a Schwartz function by showing that $I_1, \ldots, I_6 : \R \to \C$ are Schwartz functions. As mentioned in \Cref{Ch3:Prop:Multidimensional_Schwartz_of_Schwartz}, this allows us to conclude that $a : \R^8 \to \C$, defined as in \eqref{Ch4:Eq:a_def}, lies in the Schwartz space $\Sch\of{\R^8, \C}$.

%%%%%%%% END OF RESTORED TEXT

We now show that similar results hold for the $-1$-eigenfunction.

\subsection{The $-1$-Eigenfunction}

At the end of \Cref{Ch4:Subsec:b_def}, we observed striking similarities between the $J_j$ and the $I_j$. As a result, much of the proof of Schwartzness is quite similar. Our main strategy is the same: we show that $J_1, \ldots, J_6$ are Schwartz and conclude that $b\rad$ (and hence $b$) must be Schwartz as well. We emphasise the aspects that differ but do not discuss the aspects that do not in too much detail.

We begin with a discussion on why the $J_j$ are smooth. As with the proof of \Cref{Ch4:Lemma:Ij_Smooth}, we can use the Leibniz Integral Rule to reduce the problem to that of showing that the integrands of the $J_j$ are smooth. But as discussed after \Cref{Ch4:Prop:psi_as_div_disc}, the $\psi$-functions are smooth. The result is therefore immediate.

A more nontrivial step involves proving an analogue of \Cref{Ch4:Lemma:PolyFourierCoeffBound_Apply_a} for the $\psi$-functions.

\begin{boxlemma}\label{Ch4:Lemma:PolyFourierCoeffBound_Apply_b}
    There exist real numbers $C_S, C_I, C_T > 0$ such that
    \begin{align}
        \abs{\psi_S\of{z}} &\leq C_S \, e^{- \pi \Im(z)}
            \label{Ch4:Eq:PolyFourierCoeffBound_psi_S} \\
        \abs{\psi_I\of{z}} &\leq C_I \, e^{2\pi \Im(z)}
            \label{Ch4:Eq:PolyFourierCoeffBound_psi_I} % \\
        % \abs{\psi_T\of{z}} &\leq C_T \, % e^{2\pi \Im(z)} % What goes here?
        %     \label{Ch4:Eq:PolyFourierCoeffBound_psi_T} \\
    \end{align}
    for all $z \in \Halfplane$ with $\Im(z) > 1/2$.
\end{boxlemma}
\begin{proof}
    For the purposes of this proof, we will consider the $\psi$-functions to be expressed as in \Cref{Ch4:Prop:psi_as_div_disc}. We have seen in \Cref{Ch2:Subsec:ThetaFunctions} that the Fourier coefficients of the $H$-functions have polynomial growth. From \Cref{Ch4:Prop:PolyGrowth_of_mul} and the ensuing discussion, we can see that the numerators of the $\psi$-functions all admit Fourier expansions with polynomially growing coefficients. All that remains is to explicitly compute the value of $n_0$ for the numerators.
    
    Denote by $N_I$, $N_S$ and $N_T$ the values of $n_0$ for the numerators of $\psi_I$, $\psi_S$ and $\psi_T$ respectively. From \eqref{Ch2:Eq:H2_qexpansion_explicit}, we can see that $n_0\of{H_2} = 1$. Furthermore, from \Cref{Ch2:Def:Theta_H}, we can see that $n_0\of{\Theta_3} = n_0\of{\Theta_4} = 0$, from which we can conclude that $n_0\of{H_3} = n_0\of{H_4} = 0$. Finally, $c_{H_2}\of{1} = 16$ from \eqref{Ch2:Eq:H2_qexpansion_explicit} and $c_{H_2} = c_{H_3} = 1$ from \Cref{Ch2:Def:Theta_H}. We are now ready to compute $N_S$ and $N_I$.
    \begin{itemize}
        \item \underline{$N_S = 3$.} Note that $n_0\of{H_2^3} = 3$ and the smallest $n_0$ in the numerator of $\psi_S$ is $0$, with none of the $n_0$th coefficients cancelling. Hence, $N_S = n_0\of{H_2^3} = 3$. %. Since $n_0\of{H_4} = n_0\of{H_4^2} = 0$ but $n_0\of{H_2^2} = n_0\of{H_2 H_4} = 0$, we can conclude that $N_S = 3 + 0 = 3$.

        \item \underline{$N_I = 0$.} Note that $n_0\of{H_4^3} = 0$ and the smallest $n_0$ in the numerator of $\psi_I$ is $0$, with none of the $n_0$th coefficients cancelling. Hence, $N_I = n_0\of{H_r^3} = 0$.
    \end{itemize}
    Substituting these into \Cref{SP:PolyFourierCoeffBound} then yields the desired result.
\end{proof}

We are now ready to compute bounds on the $J_j$. Note that the 