\thispagestyle{empty}
\section*{Acknowledgments}

\textit{I would like to dedicate this project to my two beloved Thathas, both of whom attained Moksha during my time at Imperial. While I knew your beginnings were humble, I wish I had realised, when you were still in this world, just how much you did so that your children could have better opportunities than you. As have they, I shall ever strive to pay it forward, and completing this degree is the first step towards doing that. Not a day goes by when I do not miss you, and I will forever be grateful for all you have given me. Om Shanti.}

To my supervisor, Bhavik, I am beyond grateful for your guidance and support throughout this project. I would never have thought a chance encounter in Lausanne would lead to a working relationship that would so significantly impact my professional outlook. You have given me new standards to aspire to early on in my career, with your sharpness of mind and vastness of knowledge. Beyond a supervisor, you have been an incredible mentor and gave me great advice when I was applying to PhD positions. From the bottom of my heart, thank you.

I would further like to express my thanks to Kevin Buzzard for having not only introduced me to Lean but for never having stopped encouraging me since I attended my first Xena Project session in October 2021. I am especially grateful to you for having simultaneously hyped me up for this very high-profile project and fended off the FRO's requests to take the project public before the M4R deadline.

I would be remiss without thanking the great Maryna Viazovska herself, for whose work I have developed the profoundest appreciation over the course of this project. Even beyond that, your incredible warmth and approachability demonstrate that the greatest mathematicians are also great human beings. It has been my life's greatest honour to work with you.

I am grateful to the entire Lean community, particularly those based in London, and within that subset, those who attend Xena. I would particularly like to express my thanks to Heather Macbeth for her riveting metaprogramming sessions, one of which led to \lstinline|norm_numI|, and Edison Xie, for conversations, company, Lean brainstorming, and the occasional Michelin-star dinner.

Amma, Appa, I do not even know where I would begin. From listening to me ramble about abstract nonsense to sharing in all my joys and sadnesses, you are more than just the pillars of my world: you are my world. All I do, all I am, all I will be are because you made me so. I was blessed to be born to you.

Finally, I wish to thank everyone from my Wilkinson and maths family who has made Imperial feel like home. To my very first maths friends, Dev and Jaimin, thank you for the laughs, the vibes, and above all, for the solidarity. Without the two of you, Tarun, Krish, Arnav and Lisanne, this degree wouldn't have been nearly as fun. To the Wilkinsonians as well, from May and Amna, who have become such important figures in my life in just 8 months, to the two lights of my life, Ankita and Aarya, I am forever grateful. Before meeting you, I did not truly understand what a best friend was. Now, I have two.

Above all, I am grateful to have so much to be grateful for. \textit{Kurai ondrum illai, Kanna!}